%-------------------------
% Resume in LateX
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small #1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeItemPlain}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://quiquemartin.dev}{\Large Enrique Mart\'in Oca\~na}} & \href{mailto:quiquemartinocana@gmail.com}{quiquemartinocana@gmail.com} $|$ +44 7444 241378\\
  Bicester, Oxfordshire & \href{https://quiquemartin.dev}{quiquemartin.dev} $|$ \href{https://linkedin.com/in/enriquemaoc}{linkedin.com/in/enriquemaoc}\\
\end{tabular*}

\vspace{1pt}
\textit{\small Software engineer with 4+ years experience in C\#/.NET and React across Aston Martin F1 and Disney. Specialises in distributed systems, observability, and agentic AI. ScotlandIS Young Software Engineer of the Year 2023. UK Settled Status.}
\vspace{-10pt}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Aston Martin Aramco F1 Team}{Silverstone, UK}
      {Software Engineer}{Sep 2025 -- Present}
      \resumeSubSubheading
        {Graduate Software Engineer}{Sep 2023 -- Sep 2025}
      \resumeItemListStart
        \resumeItemPlain{Built C\# and .NET 8 simulation infrastructure orchestrating high-volume concurrent batches of diverse simulation types completing across race-weekend windows; applied OTEL auto-instrumentation to surface a post-processing bottleneck and cut simulation turnaround by \(\sim\)30\%.}
        \resumeItemPlain{Designed internal APIs, CLI tools and orchestration layers managing complex simulation models and post-processing workflows at scale.}
        \resumeItemPlain{Led delivery of a rule-driven validation engine translating F1 regulatory constraints into deterministic evaluation code, adopted across the full simulation platform.}
        \resumeItemPlain{Introduced OpenTelemetry tracing and metrics into the Grafana/Loki stack, reducing mean time-to-diagnose from \(\sim\)40 minutes to under 5 during race-weekend on-call windows.}
        \resumeItemPlain{Authored team-wide agentic AI coding standards --- Claude/Cursor configuration, context-engineering patterns, AI code-review rubrics --- adopted across a security-sensitive real-time codebase.}
        \item[]\small\textit{C\#, .NET 8, React, GraphQL, MongoDB, InfluxDB, Kafka, Docker, Kubernetes, Azure DevOps, OpenTelemetry}
      \resumeItemListEnd

    \resumeSubheading
      {Santander Global Tech}{M\'alaga, Spain}
      {Software Engineer Analyst}{Apr 2023 -- Sep 2023}
      \resumeItemListStart
        \resumeItemPlain{Built Python data pipelines aggregating and normalising financial data from disparate systems, replacing manual Excel reconciliation for \(\sim\)10 analysts.}
        \resumeItemPlain{Delivered internal dashboards (Dash/Plotly) giving finance and operations teams self-serve access to metrics previously requiring analyst requests.}
        \item[]\small\textit{Python, Pandas, Dash, Plotly, GitHub Actions}
      \resumeItemListEnd

    \resumeSubheading
      {The Walt Disney Company}{London, UK}
      {Technical Engineer Intern}{Jun 2021 -- Jun 2022}
      \resumeItemListStart
        \resumeItemPlain{Built internal tools in ASP.NET and React streamlining asset management and content delivery workflows across multiple Disney departments.}
        \resumeItemPlain{Refactored legacy C\# backend services into a modular, clean-architecture pattern, measurably improving testability and extensibility.}
        \resumeItemPlain{Shipped accessibility improvements to React front-ends (ARIA standards) and supported rollout of CI/CD pipelines across internal applications.}
        \resumeItemPlain{Worked cross-functionally with content operations, legal and engineering to gather requirements and release tooling iteratively.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Strathclyde}{Glasgow, Scotland}
      {BSc (Hons) Software Engineering --- Pass with Distinction; industrial placement at Disney}{Sep 2018 -- Apr 2023}
  \resumeSubHeadingListEnd

%--------SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages \& Frameworks}{C\#, .NET 8/10, TypeScript, JavaScript, React, Python, SQL, GraphQL}
    \resumeSubItem{Cloud \& Infrastructure}{Azure, AWS, Docker, Kubernetes (AKS), Terraform, GitHub Actions, Azure DevOps}
    \resumeSubItem{Data}{SQL Server, PostgreSQL, MongoDB, InfluxDB, vector DBs (pgvector)}
    \resumeSubItem{Messaging}{Kafka, RabbitMQ, Azure Service Bus}
    \resumeSubItem{Practices}{TDD, Clean Architecture, SOLID, DDD, CI/CD, OpenTelemetry, Grafana, Loki, Agile/Scrum}
    \resumeSubItem{AI \& Tooling}{Microsoft.Extensions.AI, Semantic Kernel, MCP (C\# SDK), RAG patterns, Claude Code, GitHub Copilot}
  \resumeSubHeadingListEnd

%-----------HONOURS \& AWARDS-----------------
\section{Honours \& Awards}
  \resumeSubHeadingListStart
    \resumeSubItem{ScotlandIS Young Software Engineer of the Year}{Winner, 2023}
    \resumeSubItem{Charles Babbage Award, University of Strathclyde}{Winner, 2023 --- best dissertation in the graduating cohort}
  \resumeSubHeadingListEnd

\vspace{2pt}
\small{Spanish (native) $\cdot$ English C1 Advanced (Cambridge) $\cdot$ UK Settled Status $\cdot$ EU citizen (Spain)}

%-------------------------------------------
\end{document}
